Classical Simulation of Quantum Error Correction in a Fibonacci Anyon Code

### 2014-12-17 fib2.tex
pushing changes from earlier.
Added two references, one to Mong et al. and one to Bonesteel & DiVincenzo.

Here we consider a full simulation of quantum error correction in a two-dimensional lattice 
system with Fibonacci anyons, a class of nonabelian anyons that are universal for quantum 
computation~\cite{Wang2010b}. Fibonacci anyons are experimentally motivated as the 
expected excitations of the $\nu=\frac{12}{5}$ fractional quantum Hall 
states~\cite{Slingerland2001}, and can also be realized in several spin 
models~\cite{Levin2005, Kapit2013, Palumbo2014}.

\stf{Describe main results and why they are badass.}

@@

>>>>

Here we consider a full simulation of quantum error correction in a two-dimensional lattice 
system with Fibonacci anyons, a class of nonabelian anyons that are universal for quantum 
computation~\cite{Wang2010b}. Fibonacci anyons are experimentally motivated as the 
expected excitations of the $\nu=\frac{12}{5}$ fractional quantum Hall 
states~\cite{Slingerland2001}, and can also be realized in several spin 
models~\cite{Levin2005, Kapit2013, Palumbo2014} and composite heterostructures~\cite{Mong2014}.

\stf{Describe main results and why they are badass. cite:~\cite{Bonesteel2012}}

@@

\stf{Is there a possibility of using MPS like Rob Pfeiffer to improve the simulations or include interactions?}
